Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-25 paper/main.tex
overhaul of structure of discussion

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize spatial perception\todo{not sure if this is just perception} in
14 subjects that were watching an audio-visual Hollywood movie and listened to
the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative
could localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on annotations
of selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.
% results: group AV
On a group level, results for a visual movie stimulus show significantly increased hemodynamic
activity spatially overlapping with a traditionally localized PPA but also extending into earlier visual
cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation restricted to the
anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provides further evidence that the PPA can be divided into
functional subregions.
% localizer substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.\todo{very bold claim to be written
in the abstract}

@@

@@

\begin{itemize}
    \item make more concise if applicable
    \item add counts of intro, results, discussion respectively
\end{itemize}

@@

\begin{itemize}
    \item -
\end{itemize}

@@

\begin{itemize}
    \item kürzen (war nicht ganz einfach)
    \item adapt captions of result tables to new phrasing in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
\end{itemize}

\noindent Discussion
\begin{itemize}
    \item umstrukturieren \& ggf. schon kürzen gemäß neuer Schwerpunktsetzung
    \item umschreiben gemäß neuer Schwerpunktsetzung
    \item mehr zum Thema VIS( "best contrast was chosen")
    \item \citep{bartels2004mapping, hasson2004intersubject}
\end{itemize}

@@

% hypo a
We hypothesize[d] that whole-brain analyses will/would reveal increased
hemodynamic activity spatially constrained \todo{i.e. not activity all over the
place} to the PPA as functionally defined by a visual localizer experiment using
pictures done with the same subjects \citep{sengupta2016extension}.

We hypothesize[d] that an exclusively auditory stimulus can/could localize
``visual area'' in individual subjects and thus possibly substitute a
block-design experiment using pictures.
% hypo b
Further, we hypothesize[d] that an exclusively auditory stimulus can/could
localize the PPA in individual subjects, and thus substitute a visual experiment
be which would be more practicable to assess brain functions in visually
impaired persons.\todo{phrasing}
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.\todo{interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

\todo[inline]{the topic anterior vs. posterior is mentioned at the end of the
intro for the first time; might be "surprising" but that is in line how the
story went (it's mentioned in the abstract though)}

@@

se\_new & noun cueing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII

@@

se\_old & noun cueing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII

@@

\subsubsection{Events related to low-level perception / perceptual confounds}

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events.\todo{actually, it was a box car of 200 ms starting
with the cut}.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

% AV design matrix
For the subsequent first level GLM analysis, the modeled hemodynamic responses
related to all movie cuts (including \texttt{no\_cut}) and six low-level
perceptual confounds (s. Table \ref{tab:av-events}) were included as regressors
in the design matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the AD stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included (s. Table \ref{tab:ao-events}).
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the AV stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to cue switches to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the AD
stimulus [and to capture variance of a possibly confounding change of the
soundscape after a cut], we implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occurred for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
correlated; and now what? -> cf. results and discussion}
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
contrasting nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory cue of switching to another
setting.

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the
    audio-visual movie (AV).
    Contrast 1-5 aim to isolate the PPA.
    Contrast 6-9 serve as negative control.
    Contrast 10 serves as control for moments when the narrator cues the
    listener about a switch of settings, events that could be correlated with a
    change of the soundscape.}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & vse\_new > vpe\_old & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
\end{tabular}
\end{table*}

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus (AD).
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

@@

\todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard; COH: imo it is
important that we do not have clusters all over the brain}

\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
yes, I know it is kinda difficult, figures will be honed at the very end}

@@

% study goal
The goal of this study was to investigate if annotated cues about the spatial
layout embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was defined using a visual localizer experiment within
the same subjects \citep{sengupta2016extension}.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses  of the movie and the audio-description (Z>3.4; p<.05, cluster
corrected) to results gained from the visual localizer.
% individual level
On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
the performance of the exclusively auditory naturalistic stimulus as a
substitute for a visual paradigm to localize the PPA.\todo{``localize''}
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template can
found at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
\todo{private collection}

@@

% AV intro
First, we analyzed data from the audio-visual movie offering a visual but
ecologically more valid stimulation.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts to a recurring setting (\texttt{vse\_new > vpe\_old})
yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

% figure group results primary AD & AV contrasts
\begin{figure*}[h!] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Black: outline of overlapping individual PPA ROIs.
        The results of audio-description's primary $t$-contrast (blue) that
        compares geometry-related nouns to non geometry-related nouns spoken by
        the audio-description's narrator (\texttt{geo, groom > all non-geo})
        are overlaid over the movie's primary $t$-contrast (blue) that compares
        cuts to a new setting with cuts to a familiar perspective
        (\texttt{vse\_new > vpe\_old})
   \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

@@

\paragraph{individual results}

@@

\todo[inline]{I tried to keep it concise but detailed; if individual contrasts
are mentioned (enumerated at the moment)}

@@

@@

\todo[inline]{individual results should be incorporated into above section;
depends on long discussion of individual results will be}

\subsubsection{AV stimulus}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
    % our audience highlighting innovative examples of data reuse may be used to
    % present compelling new findings & conclusions derived from published.
    % intro
Neuroimaging studies have parcellated the human brain into distinct functional
    areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
    is classically considered to be a higher visual area as increased
    hemodynamic activity in the PPA correlates with the perception of static
    pictures of landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize spatial
    perception\todo{not sure if this is just perception} in 14 subjects that
    were watching an audio-visual Hollywood movie and listened to the movie's
    audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative could
    localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
    general linear model (GLM) $t$-contrasts that are based on annotations of
    selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
    that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, results for a visual movie stimulus show significantly
    increased hemodynamic activity spatially overlapping with a traditionally
    localized PPA but also extending into earlier visual cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation
    restricted to the anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
    bilateral clusters in the anterior PPA of nine subjects and significant
    unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
    static pictures generalizes to the perception of spatial information
    embedded in an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provide further evidence that the PPA can be divided into functional
    subregions.
% localizer substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
    anterior part in visually impaired subjects.\todo{very bold claim to be
    written in the abstract}

@@

\noindent Generally

\begin{itemize}
    \item adopt some phrasing from the Speech-Anno-Paper
    \item there is no "cue about" in the English language? alternatives are
        "give a hint on/about", "indicate"; changes the sentences but should
        ask Alex
\end{itemize}

@@

\begin{itemize}
    \item make more concise if applicable
\end{itemize}

@@

\begin{itemize}
    \item Figure of regressor correlations: maybe write out in full the name of
        regressors (instead of pointing to the table)
\end{itemize}

@@

\begin{itemize}
    \item kürzen (war nicht ganz einfach)
    \item table of results: how many decimal points?
    \item how much details regarding procedure in Sengupta?
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
    \item check if captions of figs and tables now (really) match phrasing
        in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin

\end{itemize}

\noindent Discussion
\begin{itemize}
    \item Discussion is restructured
    \item current structure makes a lot things easier/concise/more logical to
        convey, and eventually easier to read and the message to grasp
    \item as Simon stated I would be interesting to discuss differences between
        contrasts (and make wild assumptions) but this will exceed the word
        limit by far
    \item mehr zum Thema VIS? ("best contrast was chosen")
\end{itemize}

@@

% hypo a
We hypothesize[d] that whole-brain analyses will/would reveal increased
hemodynamic activity spatially constrained to the PPA as functionally defined by
a visual localizer experiment using pictures done with the same subjects
\citep{sengupta2016extension}.

We hypothesize[d] that an exclusively auditory stimulus can/could localize
``visual area'' in individual subjects and thus possibly substitute a
block-design experiment using pictures.
% hypo b
Further, we hypothesize[d] that an exclusively auditory stimulus can/could
localize the PPA in individual subjects, and thus substitute a visual experiment
be which would be more practicable to assess brain functions in visually
impaired persons.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.\todo{interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

@@

se\_new & noun describing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII

@@

se\_old & noun describing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII

@@

\subsubsection{Events related to low-level perception / low-level perceptual
confounds}

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events.\todo{box car of 200 ms starting with the cut}.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

% AV design matrix
For the subsequent first level GLM analysis, the modeled hemodynamic responses
related to all movie cuts (including \texttt{no\_cut}) and six low-level
perceptual confounds (s. Table \ref{tab:av-events}) were included as regressors
in the design matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the AD stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included (s. Table \ref{tab:ao-events}).
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the AV stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the AD
stimulus [and to capture variance of a possibly confounding change of the
soundscape after a cut], we implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already indicate a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
correlated; and now what? -> cf. discussion, part "random shower thoughts"}
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
contrasting nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory hint of switching to another
setting.

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the
    audio-visual movie (AV).
    Contrast 1-5 aim to isolate the PPA.
    Contrast 6-9 serve as negative control.
    Contrast 10 serves as control for moments when the narrator indicates the
    a switch of settings, events that could be correlated with a
    change of the soundscape.}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & vse\_new > vpe\_old & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
\end{tabular}
\end{table*}

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus (AD).
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

@@

\todo[inline]{SE: in Figure weiter reinoomen; bei FFA/PPA etc sind
flatmaps/inflated brains standard; COH: imo it is important that we do not have
clusters all over the brain}

\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
this figure is my end game boss}

@@

% study goal
The goal of this study was to investigate if annotated hints about the spatial
layout embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses of the movie and the audio-description (Z>3.4; p<.05, cluster
corrected) to results gained from a traditional visual localizer
\citep{sengupta2016extension}.
% individual level
On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
the performance of the exclusively auditory naturalistic stimulus as a
substitute for a visual paradigm to "localize" [?] the PPA.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152 space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.  \todo{private
collection}

@@

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts to a recurring setting (\texttt{vse\_new > vpe\_old})
yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{check that}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

% figure group results primary AD & AV contrasts
\begin{figure*}[h!] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Black: outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.
        The results of audio-description's primary $t$-contrast (blue) that
        compares geometry-related nouns spoken by the narrator to non-spatial
        nouns (\texttt{geo, groom} > all non-spatial
        categories)
        are overlaid over the movie's primary $t$-contrast (blue) that compares
        cuts to a new setting with cuts to a familiar perspective
        (\texttt{vse\_new > vpe\_old}).
        }
    \label{fig:group-slices}
\end{figure*}

@@

@@

\todo[inline]{I tried to keep it concise but detailed; individual contrasts
are given but as numbers}

@@

\todo[inline]{Discussion: explains how results fill gap identified in
intro}

@@
